Generative Adversarial Networks

### 2017-12-01 cs6735/project/draft.tex
continued draft

\subsection{Label Smoothing}
\subsection{Virtual Batch Normalization}

\section{Model Variations}
Research within the field of deep generative modeling has increased exponentially since the debut of generative adversarial networks in 2014. Significant improvements are being made with image quality and new applications are being found every month.

@@

\subsection{Deep Convolutional GANs}
\subsection{Wasserstein GANs}
\subsection{Conditional GANs}
\subsection{Progrssive GANs}

>>>>

\subsection{Label Smoothing}
Label smoothing was a technique first introduced in the 1980s which involves replacing the 0 and 1 targets with \textit{smoother} values such as 0.1 and 0.9 respectively \citep{2016arXiv160603498S}. This technqiue is used to improve the networks resistance to adversarial examples. Specifically, it is recommendended to use one-sided label smoothing by using 0.9 label instead of 1 for the real data. By altering the label for fake data, this may lead to problems when $p_{data}(x)$ nears $0$ and $p_{model}(x)$ becomes large for some sample $x$ \citep{2016arXiv160603498S}.

\subsection{Virtual Batch Normalization}
Batch normalization is a technique which involves applying normalization for each training minibatch. This allows for much higher learning rates, more stable training and reduces problems associated with parameter initializtion \citep{2015arXiv150203167I}. This normalization technique was shown to successful for Deep Convolutional GANs; however, this causes a dependance relationship between the samples of the minibatch \citep{2016arXiv160603498S}...

\section{Architecture Variations}
Research within the field of deep generative modeling has increased exponentially since the debut of generative adversarial networks in 2014. Significant improvements are being made with image quality and new applications are being found every month.

@@

\subsection{Fully Connected GANs}
\subsection{Convolutional GANs}
\subsection{Inference GANs}
\subsection{Progrssive GANs}
